Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-12-17 aa workingdraft/draft.tex
Updates from Overleaf

\subsection{Residual Non-Randomness}

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=5in]{../pics/heterosked.png}
\caption{Plots of residuals and residual variance pooled from all 12 $\Rey_c$ and collector density treatments, including controls. Red lines are locally-weighted smoothing functions \textbf{(a)} Residuals of the exponential model. \textbf{(b)} Residuals of the transformed linear model used in analyses.}
\label{fig:flumevol}
\end{figure}

\subsection{Run Duration}
